On the Design, Implementation and Use of Laziness in R

### 2019-08-06 report/alien-promises.Rmd
Add context sensitive lookup, lifecycle analysis

```{r echo = TRUE, warning=FALSE, message=FALSE}
Sys.setenv("DISPLAY"=":0")

knitr::opts_chunk$set(fig.width = 12, fig.height = 4)

@@

```{r echo = TRUE, warning=FALSE, message=FALSE}
promise_alive_gc_cycles <- read_table("argument_promise_alive_gc_cycle_distribution")
```

# Promise Garbage Collection

```{r, eval = TRUE, echo = FALSE}
total_argument_promise_count <- sum(promise_alive_gc_cycles$promise_count)

datatable(promise_alive_gc_cycles)

zero_gc_cycle_promises <- 
    promise_alive_gc_cycles %>%
    filter(alive_gc_cycle == 0)

if(nrow(zero_gc_cycle_promises) == 0) {
    zero_gc_cycle_promises <- tibble(promise_count = 0, relative_promise_count = 0.0)
}

one_gc_cycle_promises <- 
    promise_alive_gc_cycles %>%
    filter(alive_gc_cycle == 1)

plus_one_gc_cycle_promises <- 
    promise_alive_gc_cycles %>%
    filter(alive_gc_cycle > 1) %>%
    summarize(promise_count = sum(promise_count)) %>%
    mutate(relative_promise_count = promise_count / total_argument_promise_count)

promise_alive_gc_cycles_graph <-
    promise_alive_gc_cycles %>%
    filter(alive_gc_cycle <= 5) %>%
    ggplot(aes(x = alive_gc_cycle, y = relative_promise_count)) +
    geom_col() +
    scale_x_discrete(limits = 0:5) +
    scale_y_continuous(sec.axis = sec_axis(~ .* total_argument_promise_count, labels = count_labels),
                       labels = relative_labels) +
    coord_flip() +
    labs(x = "", y = "")

save_local_graph(promise_alive_gc_cycles_graph, "promise_alive_gc_cycles_graph.pdf", width = 12, height = 3)

widths <- c(zero_gc_cycle_promises$promise_count, one_gc_cycle_promises$promise_count, plus_one_gc_cycle_promises$promise_count)

print(widths)
bar(widths, total_argument_promise_count, c("0", "1", "> 1")) %>%
save_local_graph("promise_gc_graph.pdf", width = 12, height = 1)
#datatable()
#
```

>>>>

```{r echo = TRUE, warning=FALSE, message=FALSE}
knitr::opts_chunk$set(fig.width = 12, fig.height = 4)

@@

```{r echo = TRUE, warning=FALSE, message=FALSE}
alien_promises_by_expression <- read_table("alien_promises_by_expression")
```

# Alien Promises

```{r, eval = TRUE, echo = FALSE}
alien_promises_by_expression %>%
datatable()
```

### 2019-08-06 report/paper-extra.Rmd
Add context sensitive lookup, lifecycle analysis

```{r echo = TRUE, warning=FALSE, message=FALSE}
knitr::opts_chunk$set(fig.width = 12, fig.height = 4)

@@

bar <- function(widths, total, labels) {
    options(device = cairo_pdf)
    ## If you want to draw arbitrary rectangles, use geom_tile() or geom_rect()
    xmin <- cumsum(c(0, head(widths, -1)))
    df <- data.frame(
        xmin = xmin,
        xmax = cumsum(widths),
        ymin = -0.5,
        ymax = 0.5,
        fill = factor(1:length(widths)),
        label = labels,
        xmid = widths/2.0 + xmin,
        ymid = 0
    )

@@

```{r echo = TRUE, warning=FALSE, message=FALSE}
alien_promises_by_expression <- read_table("alien_promises_by_expression")
```

# Alien Promises

```{r, eval = TRUE, echo = FALSE}
alien_promises_by_expression %>%
datatable()
```

>>>>

```{r echo = FALSE, warning=FALSE, message=FALSE}
knitr::opts_chunk$set(fig.width = 12, fig.height = 4)

@@

bar <- function(widths, total, labels) {
    options(device = cairo_pdf)
    ## If you want to draw arbitrary rectangles, use geom_tile() or geom_rect()
    xmin <- cumsum(c(0, head(widths, -1)))
    df <- data.frame(
        xmin = xmin,
        xmax = cumsum(widths),
        ymin = -0.5,
        ymax = 0.5,
        fill = factor(labels), #factor(1:length(widths)),
        label = labels,
        xmid = widths/2.0 + xmin,
        ymid = 0
    )

@@

```{r echo = TRUE, warning=FALSE, message=FALSE}
argument_promise_count_by_call_depth <- read_table("argument_promise_count_by_call_depth")
argument_promise_count_by_forcing_scope <- read_table("argument_promise_count_by_forcing_scope")

event_counts <- read_table("event_counts")
summarized_event_counts <- 
    read_table("summarized_event_counts") %>%
    arrange(desc(count))

extreme_event_counts <- read_table("extreme_event_counts")
event_processing_rates <- read_table("event_processing_rates")

substitute_class_summary <- read_table("substitute_class_summary")
non_same_scope_substitute_calls <- read_table("non_same_scope_substitute_calls")

promise_lifecycle_summary <- read_table("promise_lifecycle_summary")
promise_lifecycle_list <- read_table("promise_lifecycle_list")

context_sensitive_lookup_summary <- read_table("context_sensitive_lookup_summary")
context_sensitive_lookup_symbols <- read_table("context_sensitive_lookup_symbols")

promise_gc_summary <- read_table("promise_gc_summary")
promise_gc_distribution_by_type <- read_table("promise_gc_distribution_by_type")

promise_argument_forced_by_promise_argument <- read_table("promise_argument_forced_by_promise_argument")
promise_argument_returning_non_locally <- read_table("promise_argument_returning_non_locally")
```

# Events

```{r, eval = TRUE, echo = FALSE}
datatable(summarized_event_counts)

event_graph <-
    bar(summarized_event_counts$count, sum(summarized_event_counts$count), summarized_event_counts$event)

save_local_graph(event_graph, "event_graph.pdf", width=12, height=2.5)    
```

# Substitute Summary

```{r, eval = TRUE, echo = FALSE}
datatable(substitute_class_summary)

datatable(non_same_scope_substitute_calls)
```

# Promise Lifecycle

```{r, eval = TRUE, echo = FALSE}
datatable(promise_lifecycle_summary)

promise_lifecycle_list %>%
filter(argument, escaped) %>%
datatable()

promise_lifecycle_list %>%
filter(!argument, escaped) %>%
datatable()

promise_lifecycle_list %>%
filter(argument, !escaped) %>%
datatable()

promise_lifecycle_list %>%
filter(!argument, !escaped) %>%
datatable()
```

# Context Sensitive Lookup

```{r, eval = TRUE, echo = FALSE}
datatable(context_sensitive_lookup_summary)

datatable(context_sensitive_lookup_symbols)
```

# Promise GC

```{r, eval = TRUE, echo = FALSE}
datatable(promise_gc_summary)

datatable(promise_gc_distribution_by_type)
```

# Side Effects

```{r, eval = TRUE, echo = FALSE}
print("TODO")
```

# Evaluation Call Depth

```{r, eval = TRUE, echo = FALSE}
datatable(argument_promise_count_by_call_depth)

total_count <-  sum(argument_promise_count_by_call_depth$promise_count)

argument_promise_call_depth_graph <-
    argument_promise_count_by_call_depth %>%
    filter(call_depth %in% c(1:5, "> 5")) %>%
    ggplot(aes(call_depth, relative_promise_count)) + 
    geom_col() +
    scale_x_discrete(limits = c(1:5, "> 5")) +
    scale_y_continuous(sec.axis = sec_axis(~ . * total_count,
                                           labels = count_labels),
                       labels = relative_labels) +
    labs(x = "", y = "") + 
    coord_flip()

save_local_graph(argument_promise_call_depth_graph, "argument_promise_call_depth_graph.pdf", width=12, height=2.5)
```

# Mutually Forcing Argument Promises

```{r, eval = TRUE, echo = FALSE}
datatable(promise_argument_forced_by_promise_argument)
```

# Non local returning promises

```{r, eval = TRUE, echo = FALSE}
datatable(promise_argument_returning_non_locally)
```

# Promise Dispatch Force

```{r, eval = TRUE, echo = FALSE}
datatable(argument_promise_count_by_forcing_scope)
```

TODO:
- 1. Promise Evaluation Depth
- 2. Mutually forcing argument promises
- 3. Non local returning promise arguments
- 4. Validation of these cases
- 5. Fix Side Effect data and analysis
- 6. Number of promises forced by dispatch
- 7. Kind of expression in unbound promises

- 9. Add event count bar
- 8. Add time measurement to all R analyses
- 12. Move summarize outliers form summary.R to the analysis report.
      Add summarize outliers line to the report and make sure the analysis is correct.

- 10. Add figure showing data/files/time at each step of analysis
- 11. Add figure showing how reduce/combine etc. work
